Real-time Attention Assessment for Social Robots

### 2015-09-15 paper.tex
Added a few very relevant references

\subsection*{Engagement and Attention: Related Work}
The notion of engagement has actively been studied in a diverse set of domains,
and several variables and social signals have been proposed in the literature to
quantify and study it in social interactions.

@@

@@

Regarding to the approach used, some limitations need to be considered. The most
relevant one, the fact that the positions of the VFOA need to be known in
advance and defined as static \textit{tf} frames in the system. Moreover, it is
important to notice that eye gaze information is neglected which induces a
certain amount of error, as well as the noise induced by the 3D pose estimation
computed from face landmarkers.

>>>>

\subsection*{Engagement and Attention: Related Work}

\paragraph{Head Tracking and Visual Attention}

Technique for head pose estimation: based on depth
sensing~\cite{fanelli2012real}.

In our work, we rely on recent advances on template-based face
alignement~\cite{kazemi2014one} that allows fast (in the order of
a few milliseconds) face features extraction on 2D images, that we found to be fairly
robust to real-world lighting conditions and occlusions naturally occuring in child-robot
interactions.

\cite{kennedy2015head} -> it does not work!

\paragraph{Engagement}

The notion of engagement has actively been studied in a diverse set of domains,
and several variables and social signals have been proposed in the literature to
quantify and study it in social interactions.

@@

In~\cite{baxter2014tracking}, Baxter~\etal posit that the measure of the
direction and timing of gaze in child-robot interactions is a proxy for
engagement and attribution of social agency, However, they conduct these
measures as post-hoc analyses. This work suggests a path forward for real-time
assessment of engagement.

@@

Regarding to the approach used, some limitations need to be considered. The most
relevant one, the fact that the positions of the VFOA need to be known in
advance and defined as static \textit{tf} frames in the system. Moreover, it is
important to notice that eye gaze information is neglected which induces a
certain amount of error, as well as the noise induced by the 3D pose estimation
computed from face features.

In that regards, it is interesting to put this work on human-robot interaction
in perspective with previous research conducted on ape-human interaction by
Tomasello~\etal~\cite{tomasello2007reliance}: they show that apes rely primarily
on the head pose to estimate the focus of attention of a human partner, in to contrast
to human children who primarily rely on eye direction. From this perspective,
our robot mimics attention tracking mechanism comparable to the ones found in apes.
